Blueprint for efficient nuclear spin characterization in color center

### 2023-08-24 article.tex
final?

@@

@@

@@

For the presented protocol, the precision for various spins is limited by \vvv{XXX} for the S=1, for the N = 4000. \\

@@

%%%%%%%%%%%%%=========
\appendix
%%%%%%%%%%%%%=========
\section{5pESEEM formula}
\label{app:seqs}
The details of mentioned sequences in the main text can be found in fig \ref{fig:seqs}:
\begin{figure}%[htbp]
	\begin{center}
		\includegraphics[width=0.9\columnwidth]{pict/seqs.png}
		\caption{Pulse sequences a. Ramsey b. Hahn Echo c. Dynamical Decoupling d. DDESEEM}
		\label{fig:seqs}
	\end{center}
\end{figure}

@@

%pass
\bibliography{references}% Produces the bibliography via BibTeX.

>>>>

\small 

@@

\normalsize

@@

	\label{eq:approx_DD}

@@

For the presented protocol, the precision for various spins is limited by 0.09 Hz for the S=1, for the N = 4000. \\

@@

%%%%%%%%%%%%%=========
\appendix
%%%%%%%%%%%%%=========
\section{Sequences}
\label{app:seqs}
The details of mentioned sequences in the main text can be found in fig \ref{fig:seqs}:
\begin{figure}%[htbp]
	\begin{center}
		\includegraphics[width=0.9\columnwidth]{pict/seqs.png}
		\caption{Pulse sequences a. Ramsey b. Hahn Echo c. Dynamical Decoupling d. DDESEEM}
		\label{fig:seqs}
	\end{center}
\end{figure}

@@

\section{DD analysis for bispecies systems}
\label{app:bispecies}
Consider a single color center that is surrounded by two nuclear spin species. Each species has a distinct bath, which is processing with its corresponding Larmor frequency. Assuming large Larmor frequency with respect to hyperfine couplings, one can write Eq. \ref{eq:approx_DD} for two bath ($\omega_0 \approx \omega_1 \approx \omega_L$) as follows:
\begin{gather}
	\expval{\sigma_z}_{bath} \approx 1 -2 k_1^2 \sin^4(\frac{\omega_L^{(1)} \tau}{2}) -2 k_2^2 \sin^4(\frac{\omega_L^{(2)} \tau}{2})
\end{gather}
This means that two baths interfere, and the periodicity of the total bath is not straightforward any more. Hence, if there is a narrow peak next in DD signal, it can be attributed to both of the baths. To clarify the type of nuclear spins, one has to perform further experiments, e.g., in various external magnetic fields.
%pass
\bibliography{references}% Produces the bibliography via BibTeX.
